%!TEX root = final_report.tex
\section{Future Work}  

As the results of our preliminary investigations are encouraging, we would like to explore an number of additional avenues
for improving the results of our approach. In the rest of this section we discuss the potential sources of improvements and future work.

\par Firstly, there are a few options to consider while determining the structure of the
graph. The first question is whether the graph should be directed, with edges
pointing from referring document to the referred document, or undirected. 

\par The second set of questions pertain to the method to be used for inducing
the edges between the documents which serve as the vertices in the graph. Some of these questions are :

\begin{enumerate}
\item Should the edges be based solely on hyperlinks between nodes, or also based on similarity of their texts?
\item Should the edges be transitive?
\item Should we induce a dense graph with edges between most nodes, or a sparse graph with a few edges with high weights. 
\end{enumerate}

Additionally, we could induce an edge between
all documents that fall in a particular grid cell to increase locality, or
between documents in adjacent cells, to introduce smoothing.

\par A third challenge is determining the weights of edges. Intuitively, the
weight of an edge should be proportional to the similarity of the two nodes
(documents). This notion of similarity can be formalized in a number of ways.
One approach would be to take the similarity between the language models for
the two documents as the edge weights. This could be the cosine similarity,
tf-idf weighted cosine similarity, or the KL divergence score for the document pair. 
In our experiments, we use the straightforward alternative of using the 
same edge weight for all edges regardless of document similarity.

 
\par Furthermore, since each document can potentially be related to more than
one location, we can examine the performance of holding seed document label
distributions fixed versus allowing them to vary (and acquire non-zero weights
for other locations). The latter approach would allow a document label to be
influenced by related geographic locations;  for example, the distribution for
the article for Lake Austin would end up having a nonzero weight for the
location for Travis County. As suggested earlier, this might be useful in
geolocating concepts that span multiple locations.


\par Another issue that we didn't explore due to time constraints is finding the optimal parameters (for the label propagation algorithm). While the label propagation algorithm converges

\par We would also like to explore the label propagation results for a larger graph consisting of no-geotagged documents too, using
Hadoop. Apart from implementation issues, which are hopefully already dealt with in the Hadoop based implementation of Junto, a big challenge is evaluating the model performance. This is problematic since we don't have the true grid cell labels for the non-geotagged articles, if the articles can be assigned a geographic location at all.

\par Also, we want to qualitatively explore the results generated by label propagation, especially the feasibility \comment{not feasibility, what's the word?} of the distribution of labels for each test node. Specifically, we want to qualitatively confirm if the label propagation algorithm generates a sensible distribution of locations for a document even when it doesn't get the exact location right. This property that we hypothesize to hold is critical for the feasibility of integrating label propagation with textgrounder.

\par Finally, if label propagation
give promising results, we can then examine the possibility of augmenting the
pseudo- documents in language-models based approaches with the additional
information from the new documents geolocated using label propagation.

