\subsection{Label propagation}
In order to run label propagation, we first need to create a graph structure from
wikipedia articles. In our project, this graph structure is meant to be derived from the
links between articles. Specifically, the graph is to be represented using the
adjacency list notation (v -$>$ link1 link2 ...), where each vertex is a wikipedia
article and is associated with a list of vertices, which are the other Wikipedia articles that the article has outgoing links to.

However, to the best of our knowledge, such a graph representation cannot be
directly obtained from the current implementation of the textgrounder
framework, and will require additions to the preprocessing code. There is some code in place that handles the links in an article, but the extent to which this code can be reused or updated remains to be determined.

There are a few open source projects \footnote{http://haselgrove.id.au/wikipedia.htm} \footnote{https://github.com/mirkonasato/graphipedia} \footnote{http://code.google.com/p/wikipedia-netflix/wiki/WikipediaNetflix} that attempt to create this graph by parsing xml wikipedia dumps.
However, each of these projects has its idiosyncracies that makes interoperability with Textgrounder difficult. Most importantly, they all use a different scheme for generating unique article IDs than the one used in textgrounder.
For some reason, perhaps for ease of implementation, these tools use the fact that all article titles on wikipedia are unique to extract the title for each article.
They do this by sorting the article titles lexicographically (or in the order of input), and using the index of the article title in this sorted list as the article ID.
Reconciling the article IDs between the output of these tools and textgrounder is a nontrivial problem.
Furthermore, due to different preprocessing strategies (for dealing with disambiguation pages, wikipedia specific pages, external links, etc.), each of these tools generates a slightly different set of articles than the one produced by Textgrounder.

Following a conversation with Mike Speriosu and Ben Wing, we have decided to
invest some time upfront in updating the textgrounder preprocessing script to
generate this graph for us.
This is an unexpected source of delay, but we must have
a link graph before we can do any label propagation with the Junto toolkit.

An alternative, that works around this issue, is to use a fully connected graph with an edge between all pairs of articles as the input for label propagation. This is similar to the approach used in the original label propogation algorithm suggested in \cite{zhu2002learning}.
In this scenario, the performance of label propagation would depend only on the edge weights, and not on the structure of the graph.
However in this case, it's not clear to us what the edge weights for our geolocation task should be.
We believe that the usual document similarity metrics based on word
distributions are not appropriate as edge weights, since they do not directly
reflect the notion of geographical similarity.
For example, we suspect that document similarity metrics alone would not be
able to capture the fact that Austin and Houston are more geographically
similar than Austin and San Francisco.
\par
We are interested in feedback on this hypothesis, especially on whether it is worth spending some time testing it, as opposed to proceeding with modifications to the textgrounder preprocessing scripts.
