\section{Next steps}
Getting a comparison of label propagation and Textgrounder for geolocation on
the uniform grid remains our primary first step.
In order to do this, we will need to recreate the uniform case of
\cite{rolleretal:12}, which means successfully getting Textgrounder up and
running on TACC.
\par
Once we have a log file from the textgrounder run, we'll also be able to extract the cell information we
need to create labels for the label propagation system. 
\par We will also need to modify Textgrounder's existing wikipedia preprocessing scripts to have them output the link structure information. Once we have this information, we can set up label propagation so that both Junto and Textgrounder use the same training set of articles; Textgrounder for building the language models, and Junto for obtaining initial seed labels.
\par
Once Junto and Textgrounder are set up, we can run both the systems to get the predicted locations and supply these results to an evaluation mechanism.
Figuring out how to perform these steps on the simple case of uniform grid will allow us to
explore more sophisticated models, both for creating geographic cells (i.e.
using kd-trees), and for experimenting with the article graph.
\par
Once we can resolve our current technical difficulties and reach this point, we
will be able to explore questions such as how similar are the locational
predictions produced by the IR model vs. the graph-based label-propagation
model, and how useful is the additional information obtained by running label propogation over non-geotagged articles.
\par
To evaluate the performance of the models, we will use measures based on error distances, e.g., mean and median error between predicted and actual distance, instead of IR based methods like precision or recall.
\cite{rolleretal:12} show that using the centroid of locations of documents in the grid cell as the cell's location results in more accurate predictions than using the mean of document locations (as in \cite{wing-baldridge:11}), even in the uniform-grid case.
\par
The ultimate aim of this project is to get a reasonable geolocation accuracy on non-geotagged articles using Label Propgation, so that these new articles can be included in the language model for Textgrounder cells.
Once we figure out which, if any, label propagation models will work well
enough for this purpose, we can explore the possibilities made available in the
new information from the extended set.